Increasing Performance via Gamification in a Volunteer-Based Evolutionary Computation System

### 2018-01-06 2018-IPMU/Gamification/paper.tex
De-anonymizes
Revises and reduces related work, closes #6

\author{anonymous author name \inst{1} \and anonymous author name\inst{2} \and  anonymous author name \inst{1}}

\institute{anonymous institution, some city, country
\and
anonymous institution, some city, country\\
\email{example@example.edu}\\
\email{example2@example.edu}}

%\author{Mario Garc\'ia-Valdez\inst{1} \and Juan J. Merelo Guerv\'os\inst{2} \and  Lucero Lara \inst{1}}

%\institute{Instituto Tecnol\'ogico de Tijuana, Tijuana BC, Mexico
%\and
%Universidad de Granada, Granada, Spain
%\email{mario@tectijuana.edu.mx}\\
%\email{jmerelo@geneura.ugr.es}}

%\authorrunning{Garc\'ia-Valdez, Merelo, \& Lara }

@@

Distributed computing systems can be created using volunteers; these
are users who spontaneously, after receiving an invitation, decide to
provide their own resources or storage to contribute to a common
effort. They can, for instance, run a script embedded in a web page;
thus, collaboration is straightforward, but also ephemeral, with
resources depending on the amount of time the user decides to
lend. This implies that the user has to be kept engaged so as to
obtain as many computing cycles as possible. In this paper, we analyze
a volunteer-based evolutionary computing system called % NodIO
Anonymous with the objective of discovering design decisions that
encourage volunteer participation, thus increasing the overall
computing power. We present the results of an experiment in which a
gamification technique is applied by adding a leader-board showing the
top scores achieved by registered contributors. In the % NodIO
Anonymous system volunteers can participate without the need to create
an account, so one of the questions we wanted to address was if the
need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of
users created an account, those participating in the competition
provided around 90\% of the work, thus effectively increasing the
performance of the overall system.

@@

The SPACE framework \cite{leclerc2016seamless}, using a peer to peer approach, distributes fitness evaluations across a heterogeneous pool of cloud compute nodes and volunteer computers running a browser. In SPACE, peers establish a bi-directional communication with the server using the \texttt{Socket.io} JavaScript library.
As an experiment they provide an \texttt{ASM.js} compiled version of the RoboGen software platform, showing that JavaScript can be used in a broad
spectrum of applications.

@@

As indicated in the introduction, the human is an integral part of the system, which we can consider a human computation {\em human computation} \cite{quinn2011human}. Giving the user more control, and adding visibility to their participation might have positive effects. In fact, the BOINC project applies this technique by having a web page presenting the ``Top 100 multi-project BOINC participants'' in which the name of the volunteer, the number of projects, GFLOPS, country and team are displayed
(\url{https://boinc.berkeley.edu/chart_list.php}).

Next we will present the gamification technique used in this
experiment, using a system whose first version
was described in \cite{DBLP:conf/gecco/GuervosG15anom}.

>>>>

\author{Mario Garc\'ia-Valdez\inst{1} \and Juan J. Merelo Guerv\'os\inst{2} \and  Lucero Lara \inst{1}}

\institute{Instituto Tecnol\'ogico de Tijuana, Tijuana BC, Mexico
\and
Universidad de Granada, Granada, Spain
\email{mario@tectijuana.edu.mx}\\
\email{jmerelo@geneura.ugr.es}}

\authorrunning{Garc\'ia-Valdez, Merelo, \& Lara }

@@

Distributed computing systems can be created using volunteers, users who spontaneously, after receiving an invitation, decide to
provide their own resources or storage to contribute to a common
effort. They can, for instance, run a script embedded in a web page;
thus, collaboration is straightforward, but also ephemeral, with
resources depending on the amount of time the user decides to
lend. This implies that the user has to be kept engaged so as to
obtain as many computing cycles as possible. In this paper, we analyze
a volunteer-based evolutionary computing system called  NodIO
 with the objective of discovering design decisions that
encourage volunteer participation, thus increasing the overall
computing power. We present the results of an experiment in which a
gamification technique is applied by adding a leader-board showing the
top scores achieved by registered contributors. In the  NodIO
system volunteers can participate without the need to create
an account, so one of the questions we wanted to address was if the
need to register would have a negative impact on user participation.
The experiment results show that even if only a small percentage of
users created an account, those participating in the competition
provided around 90\% of the work, thus effectively increasing the
performance of the overall system.

@@

@@

As indicated in the introduction, the human is an integral part of the system, which we can consider a human computation {\em human computation} \cite{quinn2011human}. Giving the user more control, and adding visibility to their participation might have positive effects. In fact, the BOINC project applies this technique by having a web page presenting the ``Top 100 multi-project BOINC participants'' in which the name of the volunteer, the number of projects, GFLOPS, country and team are displayed.
